week getbackontrack

### 2024-11-01 clarifyRQsandDesign.Rmd
definedatafirstpush

    -   Isn't that the same question as RQ1a then?
    -   *yes and no. ;-)  this is your hypothesis for your RSiena models. whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects). \
        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*

@@

*Try to reformulate this to your RSiena model and not at your macro-level. I let you struggle a little bit on this last one okay. \
But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

*Thus **start with your descriptives and modelling \
**and rephrase RQ3 later.*

*try to **plot asap in the process**. \
and update plots after descriptives and multivariate analyses along the way. it is an iterative process.*

>>>>

    -   Isn't that the same question as RQ1a then?
    -   *yes and no. ;-)  this is your hypothesis for your RSiena models. whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).\
        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*

@@

*Try to reformulate this to your RSiena model and not at your macro-level. I let you struggle a little bit on this last one okay.\
But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

*Thus **start with your descriptives and modelling\
**and rephrase RQ3 later.*

*try to **plot asap in the process**.\
and update plots after descriptives and multivariate analyses along the way. it is an iterative process.*

### 2024-11-01 draftdata.Rmd
definedatafirstpush

---
title: "Draft-Theory"
author: "Verooo"
date: "2024-10-31"
output: html_document
bibliography: references.bib
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Theory

-   Explanation of gender homophily in scholarship

-   often: Males publishing with males, females publishing with females

-   **Hypothesis 1**: across the collaboration networks of both departments (pol. sci & soc.) scholars prefer to collaborate with same-sex scholars over different-sex scholars (gender homophily is present).

    -   [RQ1: To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University? descriptive, at network level]\

[**look at descriptives: how many men how many women in each department]**

-   Due to bias that social jobs are more feminine and politics are related to rationality, which is often stereotyped to be masculine: Expect less gender homophily in sociology than in pol.sci. department.

-   (logical error: yeah but that only makes sense if men are the only ones initiating and breaking ties, right?)

```{=html}
<!-- -->
```
-   **Hypothesis 2**: between the collaboration networks of both departments (pol. sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol. sci. department

    -   [RQ2: To what extent do the two departments differ in their gender homophily?*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].*

```{=html}
<!-- -->
```
-   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*

    -   **confusion: where would the comparison between depatments be here? this wold fit rq one more, but that one is supposed to be on the network level but this is about dyads...**

-

```{=html}
<!-- -->
```
-   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*

    -   [RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals? ego-level] *idea: whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

# References

>>>>

---
title: "draft-data"
author: "Verooo"
date: "2024-11-01"
output: html_document
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Data Draft

### 2024-11-01 draftintro.Rmd
definedatafirstpush

---
title: "Daft-Introduction"
author: "Verooo"
date: "2024-10-31"
output: html_document
bibliography: references.bib
---

@@

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

>>>>

---
title: "Daft-Introduction"
author: "Verooo"
date: "2024-10-31"
output: html_document

citation_package: apacite
bibliography: references.bib
biblio-style: apacite
natbiboptions: round
---

@@

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
klippy::klippy(color = 'darkred')
klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

### 2024-11-01 drafttheory.Rmd
definedatafirstpush

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Theory

@@

-   often: Males publishing with males, females publishing with females

@@

[**look at descriptives: how many men how many women in each department]**

@@

```{=html}
<!-- -->
```
-   **Hypothesis 2**: between the collaboration networks of both departments (pol. sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol. sci. department

    -   [RQ2: To what extent do the two departments differ in their gender homophily?*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].*

```{=html}
<!-- -->
```
-   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*

@@

-

```{=html}
<!-- -->
```
-   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*

    -   [RQ3: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals? ego-level] *idea: whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Theory Draft

@@

-   often: Males publishing with males, females publishing with females (@Horta2022)

@@

[\*\*look at descriptives: how many men how many women in each department]\*\*

@@

<!-- -->

-   **Hypothesis 2**: between the collaboration networks of both departments (pol. sci & soc.) scholars in the sociology department prefer to collaborate with same-sex scholars less strongly than scholars from the pol. sci. department

    -   [RQ2: To what extent do the two departments differ in their gender homophily?\*descriptive, at the dyad-level (after controlling for structural network effects and covariate-effects].\*

<!-- -->

-   *hypothesis for your RSiena models: whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects).*

@@

<!-- -->

-   **Hypothesis 3:** On the ego level, the preference of *men to work with men and women with women, (controlled for structural network effects), is less influential in the choice to collaborate if the alter is someone who published in a high-prestige journal.*

    -   [RQ3: How does gender homophily in collaborations between staff differ depending on scholars having published in low vs. high prestige journals? ego-level] *idea: whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

### 2024-11-01 weekbacktrack.Rmd
theorydraftfirst
definedatafirstpush

+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+

@@

+:===================================================================+:===============================================+:==============================================================+:======================================================================+:=========================================================================+:========================================================================================+:=========================================+

@@

| ![](images/used_arson%20frog.jpg)                                  | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Intro and theory [W] | ![](images/socialnetworking.jpg){width="800"}Intro and theory [W]\       | ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]                       | ![](images/Trixie-joke.jpg){width="800"} |

@@

>>>>

+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+------------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+

@@

+:===================================================================+:===============================================+:==============================================================+:=======================================================================+:=========================================================================+:========================================================================================+:=========================================+

@@

| ![](images/used_arson%20frog.jpg)                                  | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Intro and theory [W]\ | ![](images/socialnetworking.jpg){width="800"}Intro and theory [W]\       | ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]                       | ![](images/Trixie-joke.jpg){width="800"} |

@@

## ACTUAL Timeline

deadline: Saturday, 23.11.24

+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:=========================================================+
| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking_meh.jpg){width="800"}Plotting                 | ![](images/timetopanic.gif){width="800"}[chores at home] |
|                                                                                               |                                                            | [Asked Jochem for input]                                      |                                                                                            | hyp. 3                                                          |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               | Outline Intro and theory [W]\                                                              |                                                                 | Revisit RQs [D]                                                           |                                                          |
|                                                                                               |                                                            |                                                               | (missing H3 still)                                                                         | Clarify [D]\                                                    |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               |                                                                                            | & define data [S1]\                                             |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               |                                                                                            | & create effects structure [S2]                                 |                                                                           |                                                          |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday]  |
| Plotting                                                                                      |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                          |
|                                                                                               |                                                            |                                                               | Revisit RQs                                                                                |                                                                 |                                                                           |                                                          |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
| ![](images/socialnetworking_meh.jpg){width="800"}                                             | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                             |
| Data & methods part [W]                                                                       |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                          |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+
| ![](images/used_arson%20frog.jpg)[Research project course starts: little time to work on SNA] | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}Results [W]                               | ![](images/socialnetworking.jpg){width="800"}Finish Results [W] | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]  |                                                          |
|                                                                                               |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in! |                                                          |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+

![social network plot (muted) = not a lot of time for SNA, but SOME](images/socialnetworking_meh.jpg){width="80"}

![arson = otherwise busy/NO time for SNA](images/used_arson%20frog.jpg){width="80"}
:::

::: {.column width="50%"}
![time to panic = chores, admin work, and mental breakdowns/ NO time for SNA](images/timetopanic.gif){width="80"}

![kermit panicking = self-explanatory](images/kermit-panic.gif){width="80"}
:::
:::
